\label{chap:p5-tlds}
\section*{Preamble}
During the erythema study (Paper~4), weekly dose measurements were performed by placing thermoluminscent detectors (TLDs) inside patient masks in the DRS measurement area. This data was used in that paper to interpret patient responses to radiation therapy. However, since the measurements were taken every week on every patient, there was the possibility of further analysis on the collected data. TLDs are used for so many purposes across so many disciplines, that their dose response uncertainties are well understood to be around 2-3\%, depending on the calibration procedure. However, this does not address what kind of differences should be expected for repeat measurements in-phantom or \emph{in vivo}. To determine a representative uncertainty, the TLD results were statistically analyzed and a limited investigation into the source of the variation was completed.

Outside of the assistance provided for the previous paper, the majority of the work was performed by the author of this thesis (further known as ``the author''). The TLD measurements were all performed by the author, although they could not have been collected without the cooperation of the radiation therapy teams at the Juravinksi Cancer Centre (JCC). The author was trained in the use of the TLD reader and proper TLD calibration techniques by Ms. L Gamble and was supported in the endeavor by all of the members of the Physics Quality Assurance team at the JCC. The manuscript was prepared in collaboration with Dr. O. Ostapiak and was reviewed by Drs. T. Farrell and J. Hayward. The manuscript has been altered from its original form to match the style of this thesis.

\section*{Contents}

\begin{center}
	
	\textbf{Thermoluminescent dosimeter placment uncertainty in intensity-modulated radiation therapy thermoplastic masks}
	
	Diana L. Glennie, Joseph E. Hayward, Lillian Doerwald-Munoz, James Wright, and Thomas J. Farrell
	
	\textit{Department of Medical Physics and Applied Radiation Sciences, McMaster University, 1280 Main Street West, Hamilton, Ontario, L8S 1A8}
	
	\textit{AND}
	
	\textit{Department of Medical Physics, Juravinski Cancer Centre, 699 Concession Street, Hamilton, Ontario, L8V 5C2}
	
\end{center}

\noindent Submitted to the \textit{Journal of Applied Clinical Medical Physics} on DATE.

\section*{Abstract}
Text

\section{Introduction}
Text